Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-02-12 SPIE/article/main.tex
final version submitted to SPIE

\author[a,b]{Michael Weinold}
\author[b]{Sergey Kolesnikov}
\author[b,c]{Laura Diaz Anadon}
\affil[a]{Chair of Entrepreneurial Risks, ETH Zurich, Scheuchzerstrasse 7, CH-8092 Zurich, CH}
\affil[b]{Centre for Environment, Energy and Natural Resource Governance, Department of Land Economy, University of Cambridge, Cambridge, CB3 9EP, UK}
\affil[c]{Belfer Center for Science and International Affairs, Harvard Kennedy School, Harvard University, Cambridge, MA 02138, USA}

@@

We express our deep gratitude to all interviewees for their willingness to participate in this study and invaluable contributions. This research is funded by the \textit{Alfred P. Sloan Foundation}, grant number 253128. Michael Weinold further gratefully acknowledges support from the \textit{Swiss Study Foundation} of Zurich, Switzerland.

>>>>

\author[a,b]{Michael Weinold}
\author[a]{Sergey Kolesnikov}
\author[a,c]{Laura Diaz Anadon}
\affil[a]{Centre for Environment, Energy and Natural Resource Governance, Department of Land Economy, University of Cambridge, Cambridge, CB3 9EP, UK}
\affil[b]{Chair of Entrepreneurial Risks, ETH Zurich, Scheuchzerstrasse 7, CH-8092 Zurich, CH}
\affil[c]{Belfer Center for Science and International Affairs, Harvard Kennedy School, Harvard University, Cambridge, MA 02138, USA}

@@

We would like to thank Gabriel Chan, Anna Goldstein and Venkatesh Narayanamurti for many helpful discussions and their feedback. We also express our deep gratitude to all interviewees for their willingness to participate in this study and invaluable contributions. This research is funded by the \textit{Alfred P. Sloan Foundation}, grant number 253128. Michael Weinold further gratefully acknowledges support from the \textit{Swiss Study Foundation} of Zurich, Switzerland.
